Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-19 chi2012.tex
starting to cut text

\subsubsection{Results}
The participant demographic consisted of 8 people (7 male and 1 female).  They were split evenly into two age groups of 18-25 and 26-32.  All but one participant reported they used social network sites very regularly (many times a day); they said they either logged in multiple times a day, left a website page open or used dedicated application for their social networking site updates.  Those that used social networking websites primarily used Facebook.  All of the participants used Twitter to listen to broadcasted tweets, and 6 out of 8 people regularly tweeted.  The following two sections, describe the tasks people perform online with heterogeneous data and how they would use to organise a large social event.

\subsubsection{Question 1: Heterogenous Data Tasks}
All participants reported having used multiple websites to accomplish a task.  They listed example tasks such as shopping (including food, consumer electronics, hotels and flights), choosing restaurants, searching for jobs, when choosing a university, choosing recipes, study and work.  The biggest focus for shopping focused tasks was balancing price, quality and speed of delivery.  In general, people did not not trust a single websites for reviews because they said that they could be biased and did not always review the features they were interested in.  One participant said that video reviews of items were really important because they showed the aesthetics and scale of the item.  In general for initial research into organising a task it was typical to Google keywords to find related websites to their tasks.  They identified that they used different website for different jobs, such as manufacturers website for technical details, review aggregators for a range of opinions, and Google maps for location based decisions.  Social networks were also identified to have different functions, such as different groups of people belong to each and share different types of opinions.  One participant said that they shared their outlook and gmail calendars, but only for work events and did not record social activities on them.

@@

\subsubsection{Enumerated-type value consolidation}
Related to the concept of co-reference, PS.2 revealed that enumerated values of properties were often inconsistent, e.g. ``Casual dining'' vs ``Relaxed'' for a restaurant's ``atmosphere'' property. To reconcile and consolidate corresponding values from different  datasources, we extended the drag and drop support of co-reference combination to also allow users to drag and drop to combine enumerated literal values as well.

@@

% why? why were these tasks selected? can we drop in the phrase ``multi-dimensional subjective choice task'' and refer back to PS.1 to justify the choice of tasks?
We based our two tasks on choosing a university and picking a restaurant for a large social event, because in PS.1 the majority of people stated that they had used multiple websites for these tasks.  We used different two different variables for both tasks, where the restaurant was located (Glasgow and Cambridge) and which subject people choose (sport science and history).  The cities Glasgow and Cambridge were chosen because they are not geographically close to the participants, they are two heavily populated areas that have a choice of restaurants, and they contained detail data about the same restaurants on various review sites.  When deciding on which cities to use, we found that different areas favoured different review websites and places such as Hull had sets of disjoint sets of restaurant reviews.  We selected the top restaurants for on Tripadvisor and Yelp, because they were the top two websites people quoted for comparing reviews when travelling.  We selected the two university courses at random from a list taken form the complete university guide\footnote{}, and selected the top six university for that subject because they provide a realistic shortlist and are comparable in terms of rankings and properties.   We selected a shortlist of six because it is typical for users to narrow down their options to a limited selection before analysing the details of their final choice.

@@

In addition to the aforementioned feature requests, we observed a number of ``pain points'' in the design of the interface that we wish to address in the next iteration.  One such pain point was window layout and screen real estate management; participants were prone to opening up a large number of windows, including maps and charts, and found that the screen filled up very quickly.  When the screen got crowded, two problems were observed: people spent a lot of time arranging and moving windows about, and second, people tended to get lost in windows -- ``what was this again?''

\subsection{More Integration Support}

@@

\subsection{Supporting more sophisticated heterogeneity}

Supporting better structural heterogeneity:
   Combining fields
   Splitting fields
   Rearranging fields (British dates American dates)

Modelling heterogeneity (?)
   Specificity  
     Education+Jobs vs ``Education'' + ``Jobs''

   Unit conversion (kg -> stones)
   Granularity
     Crimes per area

Working with data values

>>>>

\subsubsection{Results - Heterogeneous Data Tasks}
The participant demographic consisted of 8 people (7 male and 1 female). They were split evenly into two age groups of 18-25 and 26-32.

% All but one participant reported they used social network sites very regularly (many times a day); they said they either logged in multiple times a day, left a website page open or used dedicated application for their social networking site updates.  Those that used social networking websites primarily used Facebook.  All of the participants used Twitter to listen to broadcasted tweets, and 6 out of 8 people regularly tweeted.  The following two sections, describe the tasks people perform online with heterogeneous data and how they would use to organise a large social event.
% \subsubsection{Question 1: Heterogenous Data Tasks}
All participants regularly using multiple websites to accomplish tasks.  Example of such tasks included shopping (including food, consumer electronics, hotels and flights), choosing restaurants, searching for jobs, selecting a university, seeking recipes, and finding answers to technical problems.  The biggest focus for shopping focused tasks was balancing price, quality and speed of delivery.  In general, people did not not trust single websites for reviews because they said that they could be biased and did not always review the features they were interested in.  One participant said that video reviews of items were really important because they showed the aesthetics and scale of the item.  In general, for initial research into organising a task, it was typical to use Google to search for several related websites.  They identified that they used different websites for different jobs, such as manufacturers website for technical details, review aggregators for a range of opinions, and Google maps for location-based decisions.  Social networks were also identified to have different functions, such as different groups of people belong to each and share different types of opinions.  One participant said that they shared their outlook and gmail calendars, but only for work events and did not record social activities on them.

@@

\subsubsection{Enumerated-type value consolidation}
PS.2 revealed that enumerated values of properties were often inconsistent, e.g. ``Casual dining'' vs ``Relaxed'' for a restaurant's ``atmosphere'' property. To reconcile and consolidate corresponding values from different  datasources, we extended the drag and drop support of co-reference combination to also allow users to drag and drop to combine enumerated literal values as well.

@@

% why? why were these tasks selected? can we drop in the phrase ``multi-dimensional subjective choice task'' and refer back to PS.1 to justify the choice of tasks?
We based our two tasks on choosing a university and picking a restaurant for a large social event, because in PS.1 the majority of people stated that they had used multiple websites for these tasks.  We used different two different variables for both tasks, where the restaurant was located (Glasgow and Cambridge) and which subject people choose (sport science and history).  The cities Glasgow and Cambridge were chosen because they are not geographically close to the participants, they are two heavily populated areas that have a choice of restaurants, and they contained detail data about the same restaurants on various review sites.  When deciding on which cities to use, we found that different areas favoured different review websites and places such as Hull had sets of disjoint sets of restaurant reviews.  We selected the top restaurants for on Tripadvisor and Yelp, because they were the top two websites people quoted for comparing reviews when travelling.  We selected the two university courses at random from a list taken form the complete university guide\footnote{The Complete University Guide - \url{www.thecompleteuniversityguide.co.uk}}, and selected the top six university for that subject because they provide a realistic shortlist and are comparable in terms of rankings and properties.   We selected a shortlist of six because it is typical for users to narrow down their options to a limited selection before analysing the details of their final choice.

@@

In addition to the aforementioned feature requests, we observed a number of ``pain points'' in the design of the interface that we wish to address in the next iteration.  One such pain point was window layout and screen real estate management; participants were prone to opening up a large number of windows, including maps and charts.  When their screen started to fill up, we found that participants spent a lot of time arranging windows, and second, that people tended to forget what each window represented -- ``what was this again?''.  We plan to address these issue in the next version of DataPalette.

\subsection{Integration Support}

A key design decision we made at the outset was to target the most common, simpler forms of heterogeneity we observed in PS.2.  Given the use of theinterface mechanisms we observed, we wish to next broaden the scope of capabilities of DP so that it can become more useful in real settings.  Among the integration capabilities we are considering are, first, field combination and splitting (by delimiters), in order to address the kinds of structural heterogeneity observed in several cases of PS.2, along with a framework for converting and reconciling units of measure, which would address several of the modelling issues.  Extending the Do What I Mean capabilities of the histogram and bar-charting tools to be unit-aware would be a tremendous asset, we believe, for users who want to quickly compare things without paying close attention to the units used.  A core problem to realising this, however, is that few data sources (besides the Weather category) explicitly annotated values with units used.

\subsection{Study limitations}

% \subsection{Integration Limitations}

@@
